
\documentclass[11pt]{article}
\usepackage[letterpaper,hmargin=1in,vmargin=1.25in]{geometry}
\usepackage{float}
\usepackage{abstract}
\usepackage{graphicx}
\usepackage{url}
\usepackage{subfloat}
\usepackage{indentfirst}
\usepackage{shorttoc}
\usepackage{lipsum}
\usepackage{titletoc}
\usepackage[colorlinks,linkcolor=blue,anchorcolor=blue,citecolor=green,urlcolor=black]{hyperref}
\topmargin -0.5cm \oddsidemargin 0cm \evensidemargin 0cm \textheight 22cm \textwidth 16cm
\newtheorem{Definition}{Definition}%[subsection]
\newtheorem{Theorem}{Theorem}%[subsection]
\newcommand{\F}{\mathcal{F}}
\newcommand*{\plogo}{\fbox{$\mathcal{PL}$}} % Generic publisher logo
\renewcommand{\contentsname}{\centerline{Table of content}}




\begin{document} 

\title{\LARGE\textbf{CSCI992 Professional Project \\Autumn Session 2017
\\
Code of Conduct}}
\author{}	
\maketitle
\newpage
\tableofcontents
\newpage
\setcounter{page}{1}
\pagestyle{plain}
\section{Introduction}
\par
\par
This code of conduct is used to managed our team. This code of conduct apply to all the team members in our team.
\newline
\par This code of conduct includes five topics which are team value,team ethical principles,team disciplinary actions,team standard of behaviour,team Roles and responsibilities,

\par\setlength\parindent{2em}
\par\setlength\parindent{2em}
\par\setlength\parindent{2em}	
\section{The Code} 
\subsection{Value}
Our team value is a base action and behave guideline which can give us some base principles about thinking,communicating,working,learning with everyone in the team.In detail,it will show us how to communicate with each team member,how to work with each team member,how to share and learn with each other in a multicultural,multilingual team. Our team value includes:
\begin{itemize}
\item Respect
\par\setlength\parindent{2em} We should not discriminate and respect everyone includes our team member,our classmates which may have the same team goals. 
\item Honesty
\par\setlength\parindent{2em} We should honest in our skills,abilities,knowledge,background.
\item Teamwork
\par\setlength\parindent{2em} We should work as a team and work for the same team goal.
\item Sharing
\par\setlength\parindent{2em} We should share our knowledge,learning experience with everyone in the team.
\item Learning
\par\setlength\parindent{2em}  We should learn from everyone in the team include skills,abilities,knowledge.
\item Developing
\par\setlength\parindent{2em} We should learn from everyone in the team and enhancing ourselves,developing our skills,abilities and knowledge so that we can provide more assistance to our team.
	 \end{itemize} 
\par\setlength\parindent{2em}
\subsection{Standard of Behaviour} 
The standard of behaviour is used to set up a highest standard of behaviour in team-working.
Every team member are required to act as following:
\begin{enumerate}
	\item Trust,believe and honest to every team member.
	\item respect the differences of personalities,cultural, ethnic and religious among every team member.
	\item communicate with everyone with a good manner and decent language in every  occasion.
	\item cooperate with each other and co-operate with each other.
	\item achieve a common team goals,build a healthy team culture and environment.
	\item abide by all the regulations of university and the raws in Australia.
\end{enumerate}
\par\setlength\parindent{2em}
\subsection{Discipline}
Our team will not tolerate some improper behaviour that impacts adversely on our team member and our team working activities,so our team build up some discipline principle to make sure these behaviour do not exist in our team. The discipline mainly concentrate on two aspects which are misconduct and group working activities behaviour. Every team member are required abide as following: 

	\begin{itemize}
		\item Misconduct Behaviour
		\begin{enumerate}
			\item must not discriminate, harass, bully every team member.
		\item must not insult,language attack,personal attack every team member
		\item must not isolate,exclude,abandon every team member.
	\end{enumerate}
\item Team Working Activities Behaviour
	\begin{enumerate}
	\item should use English as the only one communicate language in anytime and locations.
	\item should respect the ideas,opinions,speak of every team member.
	\item should obey the management of the team includes but not limits to assignment allocation,work distribution,role distribution.  
		\item should not late,absent for every group meeting. Every team member should tell other team members before the team meeting if you have to late or absent for the group meeting.
\end{enumerate}
	\end{itemize}
\par\setlength\parindent{2em}
\subsection{Roles and Responsibilities}
Basically,our team have two kinds of roles which are manager and team members.
	\begin{itemize}
		 \item Team member 
		 \par\setlength\parindent{2em}The responsibilities of team member is to following the leadership of the manager and achieve the common team goals.The team member responsible for:
		 \begin{enumerate}
		 	\item their actions and behaviour
		 	\item complying the Code of conduct
		 	\item supervising each other in abiding this Code of conduct
		 	\item treating other team member fairly and respectably
		 \end{enumerate}	
 \item Manager 
 \par\setlength\parindent{2em}The responsibilities of manager is to lead the team to achieve the common team goals.The manager responsible for:
 	\begin{enumerate}
  		\item ensuring that the team members comply the Code of conduct
  		     \item ensuring all team working activities are comply with relevant regulations and raws
  			\item modifying and promoting the Code of conduct and providing team with a positive role model	
  		\item taking action to prevent team member to violate this Code of Conduct
 \end{enumerate}	

   
\end{itemize}
 


\end{document}














